\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-28 paper/paper.tex
Replace figures, add captions

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{mod14km.pdf}
  \caption{Kaplan Meier estimate for drive model 14.  Bands correspond to Greenwood standard errors.}
  \label{fig1}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{mod14_example1.pdf}
  \caption{Estimated GLFP for drive-model 14 plotted on Weibull paper.  Dashed line corresponds to the median of the posterior draws; pointwise 90\% credible band is in red.  Solid line is a non-parametric estimate with pointwise 90\% uncertainty band in gray.}
  \label{fig1}
\end{figure}

@@

We can also compare the four Model fits for each drive-model individually.  For these comparisons, we use the set of parameters which maximize the marginal posterior log probability. Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model. The GLFP fit for drive-models 2, 9, 14, and 40 are presented in Figure \ref{fig:mod_comp_leg}.  The black step functions again correspond to the adjusted Kaplan-Meier estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to fit the observed failure data.  All of the GLFP models appear to produce lower estimates, relative to Kaplan-Meier, of the proportion of failed hard drives for drive-model 2, with Model 4 being in closest agreement.  For drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the nonparametric estimate quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for drive-model 40.
\begin{figure}[H]
    \centering
   \includegraphics[width=\textwidth]{mod_compare_legend}
		\caption{Estimated GLFP for 4 drive-models plotted on Weibull paper.  The solid step function is the truncated adjusted Kaplan-Meier points.  \label{fig:mod_comp_leg}} 
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{dm4-exception}
\caption{Top: Event plot for uniform random sample of 60 units of drive-model 4. Left endpoints are left-truncation times, dashed lines extending to the right indicate censoring intervals, $[t_4,i, \infty)|c_{4,i}=1$, and right endpoints without joined dashed lines are observed failure times, i.e. $t_{4,i}|c_{4,i}=0$.

Bottom: The adjusted Kaplan-Meier estimate (solid step function) substantially higher than the pointwise posterior median (dashed line; shaded region showing 90\% credible interval) due to several early failures while few were at risk.  Using the same Kaplan-Meier estimator, but only the data truncated after 2500 hours (dotted line) shows close agreement with the posterior median.}

@@

\begin{figure}
\centering
\includegraphics{dm43-shrinkage}
\caption{}
\label{fig:ex-mod-43}
\end{figure}

>>>>

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{km14-prob}
  \caption{Kaplan Meier estimate for drive model 14.  Uncertainty band correspond to pointwise standard errors (using Greenwood's formula.)}
  \label{fig1}
\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{km14-prob-plus}
  \caption{Estimated GLFP for drive-model 14 plotted on Weibull paper.  Dashed line corresponds to the median of the posterior draws; pointwise 90\% credible band is in red.  Solid line is a non-parametric estimate with pointwise 90\% uncertainty band in blue.}
  \label{fig1}
\end{figure}

@@

We can also compare the four Model fits for each drive-model individually.  For these comparisons, we use the set of parameters which maximize the marginal posterior log probability. Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

\begin{figure}[H]
{\centering
\includegraphics[width=\textwidth]{single-drive-4-Models-ex}}
\caption{Posterior median of proportion failing as a function of time under Models 1-4 for sample of drive-models, with axes scales as for Weibull probability plotting.  The solid step function is the truncated adjusted Kaplan-Meier points.}
\label{fig:mod_comp_leg}
\end{figure}

The GLFP fit for drive-models 2, 9, 14, and 40 are presented in Figure \ref{fig:mod_comp_leg}.  The black step functions again correspond to the adjusted Kaplan-Meier estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to fit the observed failure data.  All of the GLFP models appear to produce lower estimates, relative to Kaplan-Meier, of the proportion of failed hard drives for drive-model 2, with Model 4 being in closest agreement.  For drive-model 14, Models 1-3 produce lower estimates of the proportion of drives failing, and for drive-model 40, they produce higher estimates.  On the other hand, Model 4 follows the nonparametric estimate quite closely across stages of lifetime.  The differences between Models 3 and 4 and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the estimates from Model 3 and 4 are nearly identical for drive-model 40.

@@

\begin{figure}
\centering
\includegraphics{dm4-exception}
\caption{\small Top: Event plot for uniform random sample of 60 units of drive-model 4. Left endpoints are left-truncation times, dashed lines extending to the right indicate censoring intervals, $[t_4,i, \infty)$, and right endpoints without joined dashed lines are observed failure times, i.e. $t_{4,i}\mbox{, where }c_{4,i}=0$.\\ Bottom: The adjusted Kaplan-Meier estimate (solid step function) substantially higher than the pointwise posterior median (dashed line; shaded region showing 90\% credible interval) due to several early failures while few were at risk.  Using the same Kaplan-Meier estimator, but only the data truncated after 2500 hours (dotted line) shows close agreement with the posterior median.}

@@

\begin{figure}
{\centering
\includegraphics{dm43-shrinkage}}
\caption{\small Top: Event plot for all units of drive-model 4. Left endpoints are left-truncation times, dashed lines extending to the right indicate censoring intervals, $[t_{43},i, \infty)$, and right endpoints without joined dashed lines are observed failure times, i.e. $t_{43,i}\mbox{, where }c_{43,i}=0$.\\ Bottom: The solid step function correponds to the adjusted Kaplan-Meier estimate. Due to the absence of collected information about early life for this particular model,due to left-truncation, the posterior median (dashed line) follows the ``global model" (dotted line), i.e. the posterior median of proportion failing for a new drive-model, approximately until the beginning of the earliest observational period.}
\label{fig:ex-mod-43}
\end{figure}
